\huge Tor's Usability for Censorship Circumvention

### 2016-04-17 pets2017-paper/pets2017-paper.tex
insert statistical significane results

The impact of the version on success rate is (significant,not significant). 
The impact of the environment on success rate is (significant,not significant). 
% SUCCESS
% TODO: impact of version on success (chi squared?.. Serge might be wrong on this) 
% TODO: impact of env on success (chi squared?.. Serge might be wrong on this)

Talk about why we chose to assign the max time of 40 minutes to did not finish. 
The impact of the version on time to completion is (significant,not significant). 
The impact of the environment on time to completion is (significant,not significant).
Figure~\ref{fig:time_to_success_clamped}
%%% RIGHT CLAMP TIME 
% TODO:  impact of env on time to success 
% TODO: impact of version on time to success

@@

Talk about the notion of ``active time,'' which is just time not spent on the progress screen. 
The impact of the version on active time is (significant,not significant). 
The impact of the environment on active time is (significant,not significant).
%%% RIGHT CLAMP ACTIVE TIME 
% TODO:  impact of env on time to success 
% TODO: impact of version on time to success

>>>>

Talk about why we chose to assign the max time of 40 minutes to did not finish. 
The impact of the version on time to completion is (significant,not significant). 
The impact of the environment on time to completion is (significant,not significant).
Figure~\ref{fig:time_to_success_clamped}

%stats
impact of version on success: not significant (W = 5.5, p-value = 0.8248)
impact of version on time to success: not significant (W = 1399, p-value = 0.1175)

impact of env on success: not significant (Kruskal-Wallis chi-squared = 4.7059, df = 2, p-value = 0.09509)
impact of env on time to success : significant ( Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16)

@@

Talk about the notion of ``active time,'' which is just time not spent on the progress screen. 
The impact of the version on active time is significant (W = 997, p-value = 0.0001571)
The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)
